---
title: "Lab4_Copy"
author: "Michelle Cryder"
date: "October 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the Data

```{r}

av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)

av
```

## Part One: Data Tidying

The avenger data consists of ten columns for each avenger called Death[1-5] to Return[1-5]

Get the data into a format where the five columns for Death[1-5] are replaced by two columnes: Time, and Death. Time should be a number between 1 and 5 (look into the function parse_number); Death is a categorical variables with values "yes", "no" and "". Call the result deaths.

Similarly, deal with the returns of characters.

```{r}
library(tidyverse)
av1 = av %>% gather(key = Time, value = Death, c(11, 13, 15, 17, 19))
av1 = av1 %>% mutate(Time = parse_number(Time))


av2 = av %>% gather(key = Time2, value = Return, c(12, 14, 16, 18, 20))
av2 = av2 %>% mutate(Time2 = parse_number(Time2))


```

## Part Two: Validation

Each team member picks one of the statements in the FiveThirtyEight analysis and fact checks it based on the data. Use dplyr functionality whenever possible.

Upload your answers and the code to the repository. Discuss and refine answers as a team.

  + Michelle: "Out of 173 listed Avengers, my analysis found that 69 had died at least one time after they joined the team."
      + This is true. I filtered out characters that had a YES under Death1, then grouped by Name, giving 69 results. 
  
```{r}

str(av1)

onedeath = av %>% filter(Death1 == "YES") 

onedeath = onedeath %>% group_by(Name.Alias)

onedeath
str(onedeath)

```



