---
title: "lab4"
author: "Collin Loy, Michelle Cryder"
date: "October 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the data

```{r}

av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
av

```

## Part One: Data Tidying

The avenger data consists of ten columns for each avenger called Death[1-5] to Return[1-5]

Get the data into a format where the five columns for Death[1-5] are replaced by two columnes: Time, and Death. Time should be a number between 1 and 5 (look into the function parse_number); Death is a categorical variables with values “yes”, “no” and “”. Call the result deaths.

Similarly, deal with the returns of characters.

```{r}
library(tidyv)
av1 = av %>% gather(key = Time, value = Death, c(11, 13, 15, 17, 19))
av1 = av1 %>% mutate(Time = parse_number(Time))

av2 = av %>% gather(key = Time2, value = Return, c(12, 14, 16, 18, 20))
av2 = av2 %>% mutate(Time2 = parse_number(Time2))


```


## Part Two: Validation

Each team member picks one of the statements in the FiveThirtyEight analysis and fact checks it based on the data. Use dplyr functionality whenever possible.

Upload your answers and the code to the repository. Discuss and refine answers as a team.

```{r}



```

## Submission

Submission
In Canvas, submit an RMarkdown file (and the knitted html document) with:

the names of all team members that worked on the document.
a link to the github repo you were working in.
code and answers to all of the questions.
you can upload the data file, but you don’t have to
Due date: You have time until Monday at 10 pm to submit the final RMmarkdown file.

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
